Working title: Ecological network control

### 2018-06-09 paper/manuscript.Rmd
Complete figure empirical controllability with the randomisations
Close #14

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot ofsize of the minimum driver node set. The vertical dashed line indicates the meann value."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability
```

>>>>

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node set $n_D$ in the empirical networks. (b) The density distribution of the difference between the relative size of the minimum driver node set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line), or randomised the direction of control between a species pair (dark line). The vertical dashed lines indicate the median values of each distribution."}
drake::loadd(fig_emp_controllability)

g <- fig_emp_controllability %>%
  purrr::map(ggplot2::ggplotGrob)
gb <- rbind(g[[1]], g[[2]], size = "first")
gb$widths <- grid::unit.pmax(g[[1]]$widths, g[[2]]$widths)
grid::grid.newpage()
grid::grid.draw(gb)
```
